Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\textbf{23. Reviewer's Comment:}
Page 8, Hostplant use and diversification... section, Ithomiini subsection,
sixth paragraph, second sentence: replace “might not be too efficient” with 
“may be inefficient”.

\textbf{23. Response:}

\begin{quote}
\color{blue}
We reworded the sentence according to the reviewer's suggestion.
\end{quote}

\textbf{24. Reviewer's Comment:}
Page 8, Hostplant use and diversification... section, Ithomiini subsection,
sixth paragraph, third sentence: make final word plural: “switches”.

\textbf{24. Response:}

\begin{quote}
\color{blue}
We replaced the word ``switch'' according to the reviewer's suggestion.
\end{quote}

\textbf{25. Reviewer's Comment:}
Page 9, first full paragraph, first sentence: replace “hypotheses state” with
“hypotheses posit”.

\textbf{25. Response:}

\begin{quote}
\color{blue}
We replaced the word ``state'' according to the reviewer's suggestion.
\end{quote}

### 2015-01-14 MS_revised.tex
comment 25

The diffuse cospeciation hypothesis predicts almost identical ages of
insects and their hostplants, while the ``resource abundance-dependent
diversity'' and the ``escape-and-radiate'' hypotheses state that insects
diversify after their hostplants \cite{nyman2012, ehrlich1964, janz2011}.
Wheat et al. (2007)
\cite{wheat2007} found strong evidence for a model of speciation congruent with
Ehrlich and Raven's hypothesis in Pieridae butterflies due to, in
addition to the identification of a key innovation, a burst of
diversification in glucosinolate-feeding taxa shortly afterwards (with a
lag of circa 10 MY). According to a recent dated phylogeny of the
Angiosperms \cite{bell2010}, the family Solanaceae split from its sister group
about 59 (49--68) MYA and diversification started (crown group age)
around 37 (29--47) MYA. Wahlberg et al. (2009) \cite{wahlberg2009} give the ages
for origin and diversification for Ithomiini at 45 (39--53) and 37
(32--43) MYA, respectively. Thus, current evidence shows that Solanaceae
and Ithomiini might have diversified around the same time, during the
Late Eocene and Oligocene, and this would be congruent with the diffuse
cospeciation hypothesis.

>>>>

The diffuse cospeciation hypothesis predicts almost identical ages of
insects and their hostplants, while the ``resource abundance-dependent
diversity'' and the ``escape-and-radiate'' hypotheses posit that insects
diversify after their hostplants \cite{nyman2012, ehrlich1964, janz2011}.
Wheat et al. (2007)
\cite{wheat2007} found strong evidence for a model of speciation congruent with
Ehrlich and Raven's hypothesis in Pieridae butterflies due to, in
addition to the identification of a key innovation, a burst of
diversification in glucosinolate-feeding taxa shortly afterwards (with a
lag of circa 10 MY). According to a recent dated phylogeny of the
Angiosperms \cite{bell2010}, the family Solanaceae split from its sister group
about 59 (49--68) MYA and diversification started (crown group age)
around 37 (29--47) MYA. Wahlberg et al. (2009) \cite{wahlberg2009} give the ages
for origin and diversification for Ithomiini at 45 (39--53) and 37
(32--43) MYA, respectively. Thus, current evidence shows that Solanaceae
and Ithomiini might have diversified around the same time, during the
Late Eocene and Oligocene, and this would be congruent with the diffuse
cospeciation hypothesis.
